LAGOS lake depth

### 2020-11-26 tables/01_predictors.Rmd
typo fix

model_predictors <- data.frame(
  variable = names(read.csv("../data/depth_predictors.csv", 
                            stringsAsFactors = FALSE)), 
  stringsAsFactors = FALSE) %>%
  dplyr::filter(variable != "lake_maxdepth_m") %>%
  left_join(taxonomy, by = c("variable" = "col_name")) %>%
  pull(pretty) %>% na.omit() %>% as.character()

>>>>

model_predictors <- data.frame(
  variable = names(read.csv("../data/depth_predictors.csv", 
                            stringsAsFactors = FALSE)), 
  stringsAsFactors = FALSE) %>%
  dplyr::filter(variable != "lake_maxdepth_m") %>%
  left_join(taxonomy_key, by = c("variable" = "col_name")) %>%
  pull(pretty) %>% na.omit() %>% as.character()
